network_plot_work

### 2023-12-11 R/run_first/2.plot_pathway_net_example.Rmd
231211

library(ppcor)
#library(matlib)
library(psych)

#
# plot residuals and full

@@

# cand_vals <- data[,1970:2000]

##CHANGE THIS 
#make p3 interconnections stronger, 
#make p3 connect weakly to p2 through one or two nodes, 
#sparsify p2 and p3 connections

@@

#adj[which(rownames(adj) %in% baits),which(colnames(adj) %in% spikes)] <- adj[which(rownames(adj) %in% baits),which(colnames(adj) %in% c(spikes))] * W
```

@@

```{r}
#sparsify p1 p2 connections

@@

##need to know which nodes are in at least one of the conditions before here

library(igraph)

@@

@@

```{r}
# Remove edges    make this general to both types of correlations

###
g <- delete_edges(g, E(g)[which(E(g)$weight<0.55)])

# Remove any vertices remaining that have no edges
g <- delete.vertices(g, degree(g)==0)

# Assign names to the graph vertices (optional)
V(g)$name <- V(g)$name

# Change shape of graph vertices
V(g)$shape <- "sphere"

# Change colour of graph vertices
V(g)$color <- "skyblue"

@@

# ref$Feature <- gsub("_","",ref$Feature)

@@

#get metabolite and taxa info

###CHANGE THIS
#define correctly ordered VIP values  -- not actually VIP - replace with ???
# VIP <- g_b[type]

VIP <- rep(5,length(V(g)))
#VIP <-

@@

colours = c("POI" = "purple", "RP" = "orange", "URP" = "lightgreen")   ##adapt this for 3 different pathway types

@@

#edge_linetype <- round(E(g)$weight, digits = 1)

#cols_f <- colorRampPalette(RColorBrewer::brewer.pal(11, 'Spectral'))

# pdf(paste0(Sys.Date(),"_net_test.pdf"))
realplot <- ggraph(tidynet, layout = coords) + 
  geom_edge_link(aes(colour = association, alpha = weight), show.legend=FALSE) + #, linetype = association)) + 
  scale_edge_color_manual(values = edge_colours, guide = "none") +
  #scale_edge_linetype_continuous(values = edge_linetype) +
  geom_node_point(
    aes(size = VIP, color = type), show.legend=FALSE
    #size = 4
  ) +
  geom_node_point(
    aes(color = type)
    #size = 4
  ) +
  scale_color_manual(values = colours) + 
  # geom_node_text(label = id, alpha = 1, family = "mono", fontface = "bold", size = 5)+  #, fontface = "italic"

  theme_void() #+
 # theme(legend.position = "none")
# dev.off()

################################################################################

@@

# Remove any vertices remaining that have no edges
g <- delete.vertices(g, degree(g)==0)

# Assign names to the graph vertices (optional)
V(g)$name <- V(g)$name

# Change shape of graph vertices
V(g)$shape <- "sphere"

# Change colour of graph vertices
V(g)$color <- "skyblue"

@@

# ref$Feature <- gsub("_","",ref$Feature)

@@

#get metabolite and taxa info

###CHANGE THIS
#define correctly ordered VIP values  -- not actually VIP - replace with ???
# VIP <- g_b[type]

VIP <- rep(5,length(V(g)))
# #VIP <- 
# 
# 
type[which(type %in% baits)] <- "POI"
type[which(type %in% spikes)] <- "RP"

@@

badplot <- ggraph(tidynet, layout = coords) + 
  geom_edge_link(aes(colour = association, alpha = weight), show.legend=FALSE) + #, linetype = association)) + 
  scale_edge_color_manual(values = edge_colours, guide = "none") +
  #scale_edge_linetype_continuous(values = edge_linetype) +
  geom_node_point(
    aes(size = VIP, color = type), show.legend=FALSE
    #size = 4
  ) +
  geom_node_point(
    aes(color = type)
    #size = 4
  ) +
  scale_color_manual(values = colours) + 
  # geom_node_text(label = id, alpha = 1, family = "mono", fontface = "bold", size = 5)+  #, fontface = "italic"

  theme_void() #+
 # theme(legend.position = "none")
# dev.off()

  # 
  # 
  # ggraph(tidynet, layout = coords) + 
  # geom_edge_link(aes(colour = association, alpha = weight)) + #, linetype = association)) + 
  # scale_edge_color_manual(values = edge_colours) +
  # #scale_edge_linetype_continuous(values = edge_linetype) +
  # geom_node_point(
  #   aes(size = VIP, color = type),
  #   #size = 4
  # ) +
  # scale_color_manual(values = colours) + 
  # # geom_node_text(label = id, alpha = 1, family = "mono", fontface = "bold", size = 5)+  #, fontface = "italic"
  # 
  # theme_void()# +
  # # theme(legend.position = "none")

>>>>

library(ppcor)
library(psych)

#
# plot residuals and full (with tweaks for problem demonstration)

@@

@@

@@

```{r}
#randomly sparsify p1 p2 connections

@@

```{r}
library(igraph)

@@

E(g)[which(E(g)$weight<0)]$association <- "-ve"
E(g)[which(E(g)$weight>0)]$association <- "+ve"

@@

```{r}
###
g <- delete_edges(g, E(g)[which(E(g)$weight<0.55)])

# Remove nodes with no edges
g <- delete.vertices(g, degree(g)==0)

V(g)$name <- V(g)$name

@@

type <- V(g)$name
```

@@

VIP <- rep(5,length(V(g)))

@@

colours = c("POI" = "purple", "RP" = "orange", "URP" = "lightgreen")

@@

realplot <- ggraph(tidynet, layout = coords) + 
  geom_edge_link(aes(colour = association, alpha = weight), show.legend=FALSE) +  
  scale_edge_color_manual(values = edge_colours, guide = "none") +
  geom_node_point(
    aes(size = VIP, color = type), show.legend=FALSE
  ) +
  geom_node_point(
    aes(color = type)
  ) +
  scale_color_manual(values = colours) +

  theme_void()

@@

g <- delete.vertices(g, degree(g)==0)

V(g)$name <- V(g)$name

V(g)$shape <- "sphere"

@@

@@

VIP <- rep(5,length(V(g)))

@@

badplot <- ggraph(tidynet, layout = coords) + 
  geom_edge_link(aes(colour = association, alpha = weight), show.legend=FALSE) + 
  scale_edge_color_manual(values = edge_colours, guide = "none") +
  geom_node_point(
    aes(size = VIP, color = type), show.legend=FALSE
  ) +
  geom_node_point(
    aes(color = type)
  ) +
  scale_color_manual(values = colours) + 
  theme_void()
